---
title: "APM 1110: FA 3"
author: "2025041131 <- Manalaysay"
output: pdf_document
---

https://github.com/hamiangg/APM-1110---FAs-SAs

## 5.
A geospatial analysis system has four sensors supplying images.The 
percentage of images supplied by each sensor and the percentage of 
images relevant to a query are shown in the following table.

# Percentage of images supplied by each sensor
```{r}
s1 <- 15
s2 <- 20
s3 <- 25
s4 <- 40
```
# Percentage of relevant images by each sensor
```{r}
r1 <- 50
r2 <- 60
r3 <- 80
r4 <- 85
```
# Overall percentage of relevant images
```{r}
overall_r <- (.15 * .50) + (.20 * .60) +
             (.25 * .80) + (.40 * .85)
```
```{r}
 overall_r
 overall_r * 100
```
0.735 or 73.5% is the overall percentage of an image being relevant 
to the query, supplied by the four sensors.

## 6.
A fair coin is tossed twice.

# Probabilities of an event 
```{r}
P_E1 <- 2/4
P_E2 <- 2/4
P_E3 <- 2/4
```
```{r}
P_E1
P_E2
P_E3
```
# Testing pairwise independence
```{r}
P_E1_E2 <- 1/4
P_E1 * P_E2
```
```{r}
P_E1_E2
```
```{r}
P_E1_E3 <- 1/4
P_E1 * P_E3
```
```{r}
P_E1_E3
```
```{r}
P_E2_E3 <- 1/4
P_E2 * P_E3
```
```{r}
P_E2_E3
```
The three events are pairwise independent, as the probability of their 
intersection is 0.25 for each pair, while also getting 0.25 as the product
of their individual probabilities.
# Testing for mutual independence
```{R}
P_E123 <- 1/4
P_E1 * P_E2 * P_E3
```
```{r}
P_E123
```
Since 0.25 is not equal to 0.125, the three events are not mutually independent.
